A methodology for calculating active source-time functions from broadband piezoelectric sensors in the laboratory

### 2020-04-23 Article_file_Source_reconstruction.tex
Updates from Overleaf

 \author[1]{Paul A. Selvadurai \corref{cor1}}
 \ead{paul.selvadurai@sed.ethz.ch}
\author[2]{Rui Wu}
\author[3]{Claudio Madonna}

@@

@@

@@

>>>>

 \author[1]{Paul A. Selvadurai \corref{cor1}}
 \ead{paul.selvadurai@sed.ethz.ch}
\author[2]{Rui Wu}
\author[3]{Claudio Madonna}
\author[2]{Omid Moradian}

@@

Understanding wave elastodynamic waves propagate through a medium has proven to have a multitude of applications in many fields of science and engineering.  
\\

Application in material science (crack detection), biomedics (ultrasonics), \textbf{more?} 
\\
The premise is to use well-understood physics associated with wave propagation, in fluids or solids media, to probe properties and assess its state in a non-destructive manner.

@@

\begin{table}[ht]
	\centering
	\caption{Material properties of HABA CK45 steel test platen.}
	\begin{tabular}{ m{5cm} m{2cm} m{4cm}} 
		\hline  
		\bf{Parameter} 			& \bf{Symbol} 		& \bf{Value}	\\
	    Density                 & $\rho$            & 7850 kg/m$^{3}$\\
	    Shear modulus           & $\mu$             & 84 GPa \\
	    Poisson's ratio         & $\nu$             & 0.28\\
	    P wave velocity         & $V_{P}$           & 5890 m/s\\
	    S wave velocity         & $V_{S}$           & 3270 m/s\\	    
		\hline  	
	\end{tabular}
	\label{table1}
\end{table}

@@

\section*{Supplemental information}

\begin{table}[ht]
	\centering
	\caption{Material properties of Piezoelectric active source (PZT-5A).}
	\begin{tabular}{ m{5cm} m{2cm} m{4cm}} 
		\hline  
		\bf{Parameter} 		      & \bf{Symbol} 	  & \bf{Value}	\\
	   & \textit{Mechanical properties} & \\
	    Density                   & $\rho$            & 7500 kg/m$^{3}$\\
	    Poisson's ratio           & $\nu$             & 0.31\\
	    Young's modulus           & $E$               & 66 GPa\\
        Curie Point               & $T_{c}$           & 350 $^{o}$C\\  
        Mechanical quality factor &   $Q_{m}$         & 100\\
	  & \textit{Piezoelectric constants} & \\
 	  & d_{33}                   & 3.74 $\times$ 10$^{-10}$ m/V\\
 	  & d_{31}                   & -1.71 $\times$ 10$^{-10}$ m/V\\
	  & \textit{Dielectric constants} & \\
 	  & d_{33}                   & 3.74 $\times$ 10$^{-10}$ m/V\\
 	  & d_{31}                   & -1.71 $\times$ 10$^{-10}$ m/V\\

		\hline  	
	\end{tabular}
	\label{table1}
\end{table}
